Summer 2025 ToDo

### 2025-05-29 Relations/Paper/Formalization.tex
Renamed implications section to hierarchy. Updated hierarchy section.

As mentioned, the $\Inc$ property can impose a computationally demanding requirement. However, $\Inc$ is used only in Theorem 1.2.3 
and the only crucial aspect of $\Inc$ needed for the proof is that no $R$-increasing 
sequence can have an upper bound.
We establish that the equivalent properties $\RP$ and $\RPm$ are sufficient for replacing $\Inc$ in the theorem (see Subsection \ref{subsec:theorems}), 
which led us to examine the condition on $s (i)$ appearing inside $\RP$ more closely. This condition provides a generalization of the notion of a normal form, 
which we explore in detail in Section \ref{sec:Implications}.

@@

($iii$) is formalized in: 
\begin{itemize}
    \item \verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN|
\end{itemize}
As can be seen we have substituted $\gInc$ with $\gRPm$ which generalizes this theorem. We have also included the assumption that $\gSN$ 
is decidable as this property enables us 
to construct a witness for an element that either does or does not have the property $\SN$. Such a witness was necessary for our proof. \sacomment{Link to decidable in later section?}

>>>>

As mentioned, the $\Inc$ property can impose a computationally demanding requirement. However, $\Inc$ is used only in Theorem 1.2.3 
and the only crucial aspect of $\Inc$ needed for the proof is that no $R$-increasing 
sequence can have an upper bound.
We establish that the equivalent properties $\RP$ and $\RPm$ are sufficient for replacing $\Inc$ in the theorem (see Subsection \ref{subsec:theorems}), 
which led us to examine the condition on $s (i)$ appearing inside $\RP$ more closely. This condition provides a generalization of the notion of a normal form, 
which we explore in detail in Section \ref{sec:Hierarchy}.

@@

($iii$) is formalized in: 
\begin{itemize}
    \item \verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN|
\end{itemize}
As can be seen we have substituted $\gInc$ with $\gRPm$ which generalizes this theorem. We have also included the assumption that $\gSN$ 
is decidable as this property enables us 
to construct a witness for an element that either does or does not have the property $\SN$. Such a witness was necessary for our proof. 
% \sacomment{Link to decidable in later section?}

### 2025-05-29 Relations/Paper/Implications.tex
Renamed implications section to hierarchy. Updated hierarchy section.

\section{Implications}
\label{sec:Implications}

@@

% From the perspective of programming language theory, the two properties of abstract rewriting 
% systems that are most interesting are $\SN$ and $\CR$. The following hierarchies 
% show chains of implications starting from these properties.
As discussed in Subsection \ref{subsec:def} we put forward $\RP$ as an alternative for $\Inc$. It is through examining $\RP$ that 
we came to the definitions below.

@@

\begin{center}

    \begin{tikzpicture}[auto,
      arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
      % A box style
      \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]

@@

        % Draw the arrows to form a diamond
        \draw [arrowstyle] (NF) -- (SN);
        \draw [arrowstyle] (NF) -- (MF);
        \draw [arrowstyle] (MF) -- (SR);
        \draw [arrowstyle] (SN) -- (WN);
        \draw [arrowstyle] (SN) -- (SR);
        \draw [arrowstyle] (WN) -- (WR);
        \draw [arrowstyle] (SR) -- (WR);
      \end{tikzpicture}
\end{center}

The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. 
The implication from $\SN$ to $\WN$ relies on the classical decidability of the property 
of being $R$-minimal, as demonstrated in our formalization:

@@

We are interested in seeing which combination of properties a relation requires in order to be complete (that is, $\gCR$ and $\gSN$). 
The following tables show either that a given combination is complete, or the appropriate counterexample which demonstrates why 
those properties do not provide the next property on the hierarchy.

The first table explores where the properties hold locally, the second explores where the properties hold globally. Counterexamples in the 
first table assume $\WCR$ and in the second table assume $\gWCR$.
\clearpage
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\begin{table}[h!]
    \centering
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
        \hline
        \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
        \hline
        $\UNto$ &  CE-\ref{CE:4}, CE-\ref{CE:12}     & CE-\ref{CE:4}, CE-\ref{CE:7}       & $\CR$\footnotemark[1] , CE-\ref{CE:9}          & $\CR$\footnotemark[1] , CE-\ref{CE:4}            & $\CR$\footnotemark[1] , $\SN$ \\
        \hline
        $\NP$ & CE-\ref{CE:10},CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[1]  , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
        \hline
        $\MP$ & $\CR$ , CE-\ref{CE:9}    & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[2] , CE-\ref{CE:9} & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
        \hline
        $\CR$   & $\CR$, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}     & $\CR$, CE-\ref{CE:9}        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
        \hline

    \end{tabular}
    \caption{Local implications}
\end{table} 
\vspace{-1cm}
% \\[-0.5cm]
\begin{table}[h!]
    \centering
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
        \hline
        \rowcolor{gray!30}     & $\gWM$         & $\gWN$         & $\gSM$             & $\gSMandWN$        & $\gSN$ \\
        \hline
        $\gUNto$ &  CE-\ref{CE:2}, CE-\ref{CE:9}     & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[1] , CE-\ref{CE:9}          & $\gCR$, $\gSN$      & $\gCR$\footnotemark[2] , $\gSN$ \\
        \hline
        $\gNP$ & CE-\ref{CE:3} , CE-\ref{CE:9}      & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[1] , CE-\ref{CE:9}          & $\gCR$, $\gSN$      & $\gCR$\footnotemark[2] , $\gSN$ \\
        \hline
        $\gMP$ & $\gCR$ , CE-\ref{CE:9}    & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[2] , CE-\ref{CE:9} & $\gCR$, $\gSN$    & $\gCR$\footnotemark[2] , $\gSN$ \\
        \hline
        $\gCR$   & $\gCR$, CE-\ref{CE:9}     & $\gCR$, CE-\ref{CE:7}     & $\gCR$, CE-\ref{CE:9}        & $\gCR$, $\gSN$      & $\gCR$ , $\gSN$ \\
        \hline

>>>>

\section{Hierarchy}
\label{sec:Hierarchy}

@@

% From the perspective of programming language theory, the two properties of abstract rewriting 
% systems that are most interesting are $\SN$ and $\CR$. The following hierarchies 
% show chains of implications starting from these properties.
This section examines the hierarchy of ARS properties. 
In programming language theory, $\SN$ and $\CR$ constitute the essential properties that 
jointly establish completeness. 
Consequently, our analysis centers on two primary categories of properties: those associated 
with termination and those associated with confluence.
% Possibly redundant introductory paragraph

As discussed in Subsection \ref{subsec:def} we put forward $\RP$ as an alternative for $\Inc$. It is through examining $\RP$ that 
we came to the 'minimal` family of properties below. These properties help to augment our ARS hierarchy.

@@

\begin{center}
    \begin{tikzpicture}[auto,
      arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
      % A box style
      \tikzstyle{boxnode} = [draw, rectangle, text centered, minimum width=1.2cm, inner sep=3pt]

      % Title nodes
      \node[text width=4cm, align=center, font=\bfseries] at (-1.5,1) {Confluence Hierarchy};
      \node[text width=4cm, align=center, font=\bfseries] at (5,1) {Termination Hierarchy};

@@

      % Draw the arrows to form a diamond
      \draw [arrowstyle] (NF) -- (SN);
      \draw [arrowstyle] (NF) -- (MF);
      \draw [arrowstyle] (MF) -- (SR);
      \draw [arrowstyle] (SN) -- (WN);
      \draw [arrowstyle] (SN) -- (SR);
      \draw [arrowstyle] (WN) -- (WR);
      \draw [arrowstyle] (SR) -- (WR);

      % Optional: Add a separation line
      \draw[dashed] (2.0,-1.5) -- (2.0,1.5);
    \end{tikzpicture}
\end{center}

The implications in this diagram are formalized in \texttt{ARS-Implications.agda}. 
The hierarchy for confluencce requires no classical assumptions, however this is not the case for the hierarchy of terminating properties.
The implication from $\SN$ to $\WN$ relies on the classical decidability of the property 
of being $R$-minimal, as demonstrated in our formalization:

@@

Having established the hierarchies of ARS properties, we now examine which property combinations are sufficient to reverse these implications and achieve completeness. The following tables illustrate, for each property combination, whether confluence (left box) and strong normalization (right box) are obtained. Where properties cannot be derived, we provide counterexamples demonstrating the necessity of additional conditions.

The first table explores where the properties hold locally, the second explores where the properties hold globally. Counterexamples in the 
first table assume $\WCR$ and in the second table assume $\gWCR$ (as a reminder, bold text is used to indicate a property holds globally).

\clearpage
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

\begin{table}[h!]
    \centering
    {\setlength{\arrayrulewidth}{1.5pt}  % Set horizontal rule thickness
    \begin{tabular}{|>{\columncolor{gray!30}}l!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c|}
        \hline
        \rowcolor{gray!30} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WM$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WN$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SM$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SMandWN$} & \multicolumn{2}{c|}{$\SN$} \\
        \hline
        $\UNto$ & CE-\ref{CE:4} & CE-\ref{CE:12} & CE-\ref{CE:4} & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$\footnotemark[1] & CE-\ref{CE:4} & $\CR$\footnotemark[1] & $\SN$ \\
        \hline
        $\NP$ & CE-\ref{CE:10} & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
        \hline
        $\MP$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[2] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
        \hline
        $\CR$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$ & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$ & $\SN$ \\
        \hline
    \end{tabular}}
    \caption{Local implications}
\end{table}
\vspace{-1cm}
% \\[-0.5cm]
\begin{table}[h!]
    \centering
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
        \hline
        \rowcolor{gray!30}     & $\gWM$         & $\gWN$         & $\gSM$             & $\gSMandWN$        & $\gSN$ \\
        \hline
        $\gUNto$ &  CE-\ref{CE:2}, CE-\ref{CE:9}     & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[1] , CE-\ref{CE:9}          & $\gCR$, $\gSN$      & $\gCR$\footnotemark[2] , $\gSN$ \\
        \hline
        $\gNP$ & CE-\ref{CE:3} , CE-\ref{CE:9}      & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[1] , CE-\ref{CE:9}          & $\gCR$, $\gSN$      & $\gCR$\footnotemark[2] , $\gSN$ \\
        \hline
        $\gMP$ & $\gCR$ , CE-\ref{CE:9}    & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[2] , CE-\ref{CE:9} & $\gCR$, $\gSN$    & $\gCR$\footnotemark[2] , $\gSN$ \\
        \hline
        $\gCR$   & $\gCR$, CE-\ref{CE:9}     & $\gCR$, CE-\ref{CE:7}     & $\gCR$, CE-\ref{CE:9}        & $\gCR$, $\gSN$      & $\gCR$ , $\gSN$ \\
        \hline
